Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-17 paper_jasa.tex
fig 10 - boundaries in y direction are 0,1

It is really curious to see in the results of experiment 3 that the power of the visual test  high independent of effect size. 
These results are based on whether the subject correctly picked the actual data plot, regardless of reason. Although subjects were asked to select the plot that exhibited the highest association between the two variables, they might have cued in on the cluster of contaminated data. This will be explored further in Section \ref{sec:TypeIII}.

@@

%Different subjects are expected to have different skill levels in evaluating lineups. This is accounted for in the mixed effects model (Equation \ref{eqn:mixed}).   
 The estimated subject-specific power curves are shown in \blue{Figure \ref{fig:power_mixed_subject} (light grey lines). The blue curve is the overall} average power estimated from the model, and for comparison, the grey dashed lines are the power curves for the conventional test. Subject-specific power is quite different for three experiments. In experiment 1 subjects performed similarly, and substantially worse than the conventional test. In experiment 2 there is more variability between subjects, with some doing better than the conventional test on small effects. In experiment 3 there is the most subject-specific variation. Some subjects performed substantially better than the conventional test, and on average the visual test was better.

>>>>

Results of experiment 3 are curious insofar, as  power of the visual test is  high independent of effect size. However, these results are based on correct identification of the actual data plot, regardless of reason. Although subjects were asked to select the plot that exhibited the highest association between the two variables, they might have cued in on the cluster of contaminated data. This will be explored further in Section \ref{sec:TypeIII}.

@@

%Different subjects are expected to have different skill levels in evaluating lineups. This is accounted for in the mixed effects model (Equation \ref{eqn:mixed}).   
\noindent The estimated subject-specific power curves are shown in \blue{Figure \ref{fig:power_mixed_subject} (light grey lines). The blue curve is the overall} average power estimated from the model, and for comparison, the grey dashed lines are the power curves for the conventional test. Subject-specific power is quite different for three experiments. In experiment 1 subjects performed similarly, and substantially worse than the conventional test. In experiment 2 there is more variability between subjects, with some doing better than the conventional test on small effects. In experiment 3 there is the most subject-specific variation. Some subjects performed substantially better than the conventional test, and on average the visual test was better.
